Binary companions of evolved stars in \apogee\ \DR: \\ Search method and catalog of $\sim$5,000 companions

### 2018-04-12 paper/1-catalog/twoface-catalog.tex
PL comments

If there are only a few radial-velocity epochs per star, and if the companion
spectrum is not observed, the data will be consistent with many different
combinations of (primary) orbital parameters (period, amplitude, eccentricity,
etc.).
To identify companions to the typical star observed in a spectroscopic survey,
we therefore face at least one major challenge: how, given a small number of
observations of a primary star, do we reliably obtain posterior information
about the binary-system properties?
In general, the likelihood function---and the posterior probability distribution
function (\pdf) under any reasonable prior \pdf---will be highly multimodal, and
many of the modes will have comparable integrated probability density.
For example, with just two radial-velocity measurements, a harmonic series of
period modes will exist in the likelihood function.

@@

DWH was partially supported by the NSF (grant AST-1517237).
HWR acknowledges support by Sonderforschungsbereich SFB 881 (A3) of the German
Research Foundation (DFG), and from the European Research Council under the
European Union’s Seventh Framework Programme (FP 7) ERC Grant Agreement
n. [321035].
DAGH and OZ acknowledge support provided by the Spanish Ministry of Economy and
Competitiveness (MINECO) under grant AYA-2017-88254-P.

>>>>

If there are only a few radial-velocity epochs per star, and if the companion
spectrum is not observed, the data will be consistent with many different
combinations of primary orbital parameters (period, amplitude, eccentricity,
etc.).
To identify companions to the typical star observed in a spectroscopic survey,
we therefore face at least one major challenge: how, given a small number of
observations of a primary star, do we reliably obtain posterior information
about the binary-system properties?
In general, the likelihood function---and the posterior probability distribution
function (\pdf) under any reasonable prior \pdf---will be highly multimodal, and
many of the modes will have comparable integrated probability density.
For example, with just two radial-velocity measurements, a harmonic series of
period modes will exist in the likelihood function.

@@

DWH was partially supported by the NSF (grant AST-1517237).
HWR acknowledges support by Sonderforschungsbereich SFB 881 (A3) of the German
Research Foundation (DFG), and from the European Research Council under the
European Union’s Seventh Framework Programme (FP 7) ERC Grant Agreement
n. [321035].
PL was partly funded by "Programa de Iniciaci\'on en Investigaci\'on –
Universidad de Antofagasta."
DAGH and OZ acknowledge support provided by the Spanish Ministry of Economy and
Competitiveness (MINECO) under grant AYA-2017-88254-P.
